Widespread nitrous oxide undersaturation in U.S. lakes and reservoirs

### 2023-03-23 manuscript/manuscript_file.Rmd
Resolved issue with fetching graphics. Added infrastructure for references.

---
title: "Widespread nitrous oxide undersaturation in U.S. lakes and reservoirs"
output: word_document
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

@@

## Introduction

## Results and Discussion

@@

```{r echo=FALSE, fig.cap= "Location of sampling sites.  Color of the points indicates whether the waterbody was functioning as a source or sink of nitrous oxide (N~2~O).  Point size indicates the dissolved N~2~O concentration"}

# [3/9/2023] knitr can only find the file if placed in the root of the RStudio project.  Why can't it pull the figure from the manuscript_figures folder?
#knitr::include_graphics("manuscript_figures/figure1.png")
```

>>>>

---
title: "Widespread nitrous oxide undersaturation in U.S. lakes and reservoirs"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
bibliography: references.bib
link-citations: yes
---

@@

# Introduction

# Results and Discussion

@@

![Location of sampling sites.  Color of the points indicates whether the waterbody was functioning as a source or sink of nitrous oxide (N~2~O).  Point size indicates the dissolved N~2~O concentration.](manuscript_figures/figure1.png)

Here is a citation example: Multilevel models are useful for survey inference [@Kennedy_Gelman_2021]. This paper by @Kennedy_Gelman_2021 provides a nice worked example.

# References
